Music Classification Using Convolutional Neural Networks

### 2019-12-15 docs/paper.tex
Correct grammar errors

\begin{abstract}
	In this paper we describe a convolutional neural network designed to classify music by genre.
	The base idea came from an article we read about the combination of CNN and mathematical algorithms for a music classification \cite{sample}.
	At the moment the network can categorise at a 61\% accuracy.
	We use the GTZAN dataset with slight modifications as it covers all our needs.
	During the building of this network we encountered numerous challenges, especially with the activation functions.
	A constant problem was overlearning, which we could only delay. 
\end{abstract}

@@

    We went through numerous iterations and tried various convolutional neural
    network architectures during development. At first we tried to use convolutional
    windows that would overlap the whole frequency domain and move only in the time domain,
    since although spectrograms can be regarded as arbitrary two dimensional data, the two
    axises have different meanings. This path led nowhere, the model was not able to
    overfit on a small subset of the dataset. We decided to use simple, rectangular convolutional
    windows, which could be called standard by now. This approach was indeed able to overfit, meaning
    it was worth to try learning on the whole dataset. Validation error would cease to decrease
    after the first few epochs. This would be followed by decreasing the input size of the model
    by splitting the samples of 30 seconds length into 4 smaller fragments.

@@

    \paragraph{Optimizer}
    The optimizer algorithm used during training was Stochastic Gradient Descent with a learning rate of 0.01.
    At first we've tried with \emph{Adam} but it did not perform quite as expected. The next choice
    was \emph{Adadelta} which showed promising results, but it did not appear to stable due to the
    fluctuation we have observed on both the graphs of training and validation accuracy.

>>>>

\begin{abstract}
	In this paper we describe a convolutional neural network designed to classify music by genre.
	The base idea came from an article we read about the combination of CNN and mathematical algorithms for music classification \cite{sample}.
	At the moment the network can categorise at a 61\% accuracy.
	We use the GTZAN dataset with slight modifications as it covers all our needs.
	During the building of this neural network we encountered numerous challenges, especially with the activation functions.
	A constant problem was overlearning, which we could only delay. 
\end{abstract}

@@

    We went through numerous iterations and tried various convolutional neural
    network architectures during development. At first we tried to use convolutional
    windows that would overlap the whole frequency domain and move only in the time domain,
    since although spectrograms can be regarded as arbitrary two dimensional data, the two
    axises have different meanings. This path led nowhere, as the model was not able to
    overfit on a small subset of the dataset. We decided to use simple, rectangular convolutional
    windows, which could be called standard by now. This approach was indeed able to overfit, meaning
    it was worth to try learning on the whole dataset. Validation error would cease to decrease
    after the first few epochs. This would be followed by decreasing the input size of the model
    by splitting the samples of 30 seconds length into 4 smaller fragments.

@@

    \paragraph{Optimizer}
    The optimizer algorithm used during training was Stochastic Gradient Descent with a learning rate of 0.01.
    At first we've tried with \emph{Adam} but it did not perform quite as expected. The next choice
    was \emph{Adadelta} which showed promising results, but it did not appear to stabilize due to the
    fluctuation we have observed on both the graphs of training and validation accuracy.
